Reproducible Research: Peer Assessment 1

The first step in the assignment is to load the data
The code as follows:
```{r Loading the Data}
# Loading 
## Setting the working directory
setwd("D:/A Reproducible Research/Peer Assessment 1/data/")
DataSet<-read.csv("activity.csv", header=,T, sep=',', nrows=17568, stringsAsFactors=F, check.names=F, comment.char="", quote='\"')
```

After loading the original data from file "activity.csv", we can now prepare a subset
```{r correcting Date and time for usual formating}
# Preprocessing the data: "correcting" Date and time for usual formating
DataSet$date <- as.Date(DataSet$date, format="%Y-%m-%d")
```
Using a matrix to simplifly the process
```{r}
Tabela<-matrix(nrow=61, ncol=4)
guarda=(DataSet$date[1]); 
numero=0; 
soma=0;
index<-1;
for (i in 1:17568) {
        if (guarda != DataSet$date[i]) { Tabela[index, 1] <-guarda;
                                         Tabela[index, 2] <-as.numeric(soma);
                                         Tabela[index, 3] <-numero;
                                         guarda <- DataSet$date[i];
                                         Tabela[index, 4] <-as.numeric(soma)/numero;
                                         numero=0; 
                                         soma=0;
                                         index<-index + 1;
        }
        if (!is.na(DataSet$steps[i])) {soma <- soma + DataSet$steps[i]}  
        numero<- numero + 1; 
}
##
```

Answering the first question: What is mean total number of steps taken per day?
For this answer, we made a plot of the total number of steps taken each day in the table above

``` {r Loading ggplot2 and plotting}
library(ggplot2)
g <- qplot(as.Date(Tabela[,1]), as.numeric(Tabela[,2]))
#
```

Now, ussing R funcrions to calculate and report the mean and median
```{r results="hide"}
mean(as.numeric(Tabela[,2]))
median(as.numeric(Tabela[,2]))
##
```
The results are:
> sum (as.numeric(Tabela[,2]))
[1] 570608
> mean(as.numeric(Tabela[,2]))
[1] 9354.23
> median(as.numeric(Tabela[,2]))
[1] 10395

